Wavelength convergence of the $\exb$ staircase pattern in flux tube simulations of ion temperature gradient driven turbulence

### 2023-03-19 briefcommunicaton/briefcommunication.tex
#37: removed \textemdash

% introduces the term basic mode of the pattern for later usage
In general, the zonal flow mode that dominates the $\exb$ staircase pattern, \textemdash also referred to as the \textit{basic mode } of the pattern in this work \textemdash exhibits the maximum amplitude in the spectrum $|\hatwexb|_{k_\mathrm{j}}$.

>>>>

% introduces the term basic mode of the pattern for later usage
In general, the zonal flow mode that dominates the $\exb$ staircase pattern, also referred to as the \textit{basic mode} of the pattern in this work,exhibits the maximum amplitude in the spectrum $|\hatwexb|_{k_\mathrm{j}}$.
